---
title: "Working with Large Dataset"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{backfile}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

One of the limitations of the EIA API is the 5000 observations limit per call. This could be challenging if you are trying to pull hourly time series, which is roughly 26280 observations per year. The `eia_backfill` function solves this issue and removes the API number of observations per call limit. On the backend, the function splits the query into multiple sequential queries, pulls the data, and returns an append object.

For example, let's pull hourly generation of electricity by New York Independent System Operator on sub-region West using the `eia_backfill` function:


```{r setup}
library(EIAapi)

 start <- as.POSIXlt("2018-06-19T00", tz = "UTC")
 end <- lubridate::floor_date(Sys.time()- lubridate::days(2), unit = "day")
 attr(end, "tzone") <- "UTC"
 offset <- 5000
 api_key <- Sys.getenv("eia_key")
 api_path <- "electricity/rto/region-sub-ba-data/data/"

 facets = list(parent = "NYIS",
               subba = "ZONA")
 
  df <- eia_backfill(start = start,
                end = end,
                offset = offset,
                api_key = api_key,
                api_path = api_path,
                facets = facets)
```

As you can see below, the return series has more than 45,000 observations:

```{r fig.height=5, fig.width=8}
head(df)

nrow(df)

at_y <- pretty(df$value)[c(2, 4, 6)]
 at_x <- seq.POSIXt(from = start,
                  to = end,
                  by = "2 years")
 plot(df$time, df$value,
      col = "#1f77b4",
      type = "l",
      frame.plot = FALSE,
      axes = FALSE,
      panel.first = abline(h = at_y, col = "grey80"),
      main = "NY Independent System Operator (West) - Hourly Generation of Electricity",
      xlab = "Source: https://www.eia.gov/",
      ylab = "MegaWatt/Hours")

 mtext(side =1, text = format(at_x, format = "%Y"), at = at_x,
       col = "grey20", line = 1, cex = 0.8)

 mtext(side =2, text = format(at_y, scientific = FALSE), at = at_y,
       col = "grey20", line = 1, cex = 0.8)
```


